Gravitational Lens Modelling in a Citizen Science Context

### 2014-10-08 text/ms.tex
unchecked edits

Modelling with \spl involves three stages, markup of the image,
followed by intensive numerical computation carried out on a
server in the background, followed by review
of diagnostics and possible discussion.  We now describe each of
these.

>>>>

Modelling with \spl involves three stages, (1)~markup of the image,
followed by (2)~intensive numerical computation carried out on a
server in the background, followed by (3)~review of diagnostics and
possible discussion.  Human interaction is essential to the first and
third stages, while stage~2 is completely automated. We now describe
the three stages.
